---
title: "xwas demo"
#author: "Nam Pho"
#date: "May 10, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Setup

Skipping over these details for now. Assume you have compiled the library from latest Github source. Future will be CRAN (hopefully). The default build puts it into `~/.R_libs/xwas/` and assumes your R library is set accordingly.

```{r}
.libPaths()
```

Now you can load the `xwas` package and are good to go if no errors.

```{r}
library(xwas)
```

Further validate by checking the `sessionInfo()` outputs.

```{r}
sessionInfo()

"xwas" %in% loadedNamespaces()
```

## 2. Package Survey

Fully documented library and functions.

```{r}
help(xwas)
```

Load included NHANES datasets for downstream analyses.

```{r}
data(nhanes)
```

## 3. Do Analysis

```{r}
xlm(data=nhanes, depvar="LBXGLU", varname="LBXGTC", adjvars=c("female", "RIDAGEYR"), permute=10)
```

Future speed ups.

```{r}
#system.time(xwas(data=nhanes, depvar="LBXGLU", permute=10, n=1))
#system.time(xwas(data=nhanes, depvar="LBXGLU", permute=10, n=4))
```
